---
title: "Hw01-xuening-hu"
output: github_document
---

### Set up working directory for all chunks 
```{r setup}
knitr::opts_chunk$set(root.dir = "/Users/Xuening/STAT133/stat133-hws-fall17/hw01")
```
```{r}
getwd()

load("nba2017-salary-points.RData")
ls()
```

##Question 1)
```{r}
# salary in million
salary_m = as.numeric(format(round(salary / 1000000,2),nsmall <- 2))
# replace R by 0
experience_int = replace(experience, experience == "R", "0")
#new position factor
position_factor = factor(position, labels = c("center", "power_fwd", "point_guard", "small_fwd", "shoot_guard"))
#frequency table
table(position_factor)
```

##Question 2)
```{r}
plot(points, salary_m, cex = 0.7, col = "red", main = "Scatterplot of Points and Salary")
```

##Question 3)
```{r}
n = length(player)

mean_points = mean(points)
mean_points = sum(points)/n

mean_salary = mean(salary_m)
mean_salary = sum(salary_m)/n

var_points = var(points)
var_points = sum((points - mean_points) ^ 2) / (n - 1)

var_salary = var(salary_m)
var_salary = sum((salary_m - mean_salary) ^ 2) / (n - 1)

sd_points = sd(points)
sd_points = sqrt(var_points)

sd_salary = sd(salary_m)
sd_salary = sqrt(var_salary)

cov_points_salary = cov(points, salary_m)
cov_points_salary = sum((points - mean_points) * (salary_m - mean_salary)) / (n - 1)

cor_points_salary = cor(points, salary_m)
cor_points_salary = cov_points_salary / (sd_points * sd_salary)
```

##Question 4)
```{r}
b1 = cor_points_salary * (sd_salary / sd_points)
b0 = mean_salary - b1 * mean_points
y_hat = b0 + b1 * points

summary(y_hat)
```

+SO the regression equation is salary = `r b0` + `r b1` * points . For increasing of each 1 unit, the salary increase  by `r b1` unit. When points = 0, salary = `r b0`. 

+The predicted salary is the folloing:
```{r, echo=FALSE}
b0 + b1 * 0
b0 + b1 * 100
b0 + b1 * 500
b0 + b1 * 1000
b0 + b1 * 2000
```

##Question 5)
```{r}
plot(points, salary_m, abline(b0, b1, col = "red", lwd = 2), col = "gray", cex = 0.7, lwd = 0.7, main = "Regression and lowess lines")
lines(lowess(points, salary_m))
text(x = 2000, y = 30, labels = "lowess")
text(x = 2300, y = 15, labels = "regression", col = "red")
```

##Question 6)
```{r}
# residual
r_residuals = salary_m - y_hat
summary(r_residuals)
# residual sum of squares
rss = sum(r_residuals * r_residuals)
# total sum of squares
tss = sum((salary_m - mean_salary) * (salary_m - mean_salary))
# coefficient of determination
rsquare = 1 - rss / tss
```

##Question 7)
```{r}
plot(experience_int, salary_m, ylab = "salary", xlab = "years of experience", cex = 0.7, col = "grey", main = "scatterplot with lowess smooth")
lines(lowess(experience_int, salary_m), lwd = 2.5, col = "red")
```

```{r}
install.packages("scatterplot3d", repos = "http://cran.us.r-project.org")
library(scatterplot3d)
scatterplot3d(x = points, y = salary_m, z = experience_int, color = "blue", main = "3D Scatterplot", ylab = "year of experience", zlab = "salary(millions)")

boxplot(salary_m~position_factor)
```

+ Description and analysis for the plots here
  + the more point in player scores, the more salary he gets.

##Question 8)
+ What things were hard
    + Utilizing the parameters and adjust the plots
+ What things were easy
   
+ Experience with git: useful
    + Keep track of every commit
    + Cooperation
+ Help for the assignment? Yes.
    + Help with some usage of functions
+ How much time
    + More than 6 hours
+ Most time consuming part
    + Graph
+ Anything not understood
    
+ Frustrating?
    + None
+ Exciting?
    + Struggling instead...